### 2020-12-13 README.Rmd
add proto version of dyad-year function
this and that, these and those

- `make_stateyears()`: converts Correlates of War or Gleditsch-Ward state membership data into state-year format.

>>>>

- `create_stateyears()`: converts Correlates of War or Gleditsch-Ward state membership data into state-year format.
- `create_dyadyears()`: converts Correlates of War or Gleditsch-Ward state system membership data into dyad-year format.
